---
title: "TASK1_LINEAR REGRESSION"
author: "EMMADISHETTI TEJASWI"
date: "16/02/2021"
output: html_document
---
Task1-Prediction using Supervised Machine Learning

GRIP @ The Sparks Foundation

# Objective: The task is to predict the percentage score of a student based on the number of study hours of that particular student. 
# This is a simple linear regression analysis task which involves only two variables.

```{r}
#setting my working directory
setwd("C:/Users/EMMADISHETTI TEJASWI/Desktop/tsf")
```

# Importing Dataset
```{r}
student<- read.csv("Data.csv",header=TRUE)
print("Data reading Successfully Done")
dim(student)
head(student)
```
# The given data consists of the Study Hours of a number of students with their respective Percentage Scores they have obtained in their exam. 
# Using this data,we can predict whether studying for more hours results in good percentage score in the exam or not.
```{r}
student
str(student)
```

# Plot the distribution of scores &  Train the linear regression model using lm function
```{r}
plot(x = student$Hours, y = student$Scores,xlab = "Hours Studied", ylab = "Percentage Score",
     col="red",xlim=c(0,10),ylim=c(0,100),main = "Percentage Scored vs Hours Studied",sub="Data of 25 persons")

student_model<-lm(Scores ~ Hours, data = student)
# Checking Model Coefficents
student_model
# Put Regression line on graph
abline(student_model, col="blue",lwd=2)
```

# Summary Of Model
```{r}
summary(student_model)
```
# R-2 gives the score of model fit and in this case we have R-2 = 0.95 which is actually a great score for this model.
```{r}
# Showing the model fitted value
fitted(student_model)
# Showing the extract model residuals
residuals(student_model)
```
# Computing the predicted results
```{r}
study_hour<-data.frame(Hours = 9.25)
predicted_score<-predict(student_model, study_hour)
print(predicted_score)
```
# Predicted score for a student studying 9.25 hours is 92.90










